\documentclass[12pt]{article}                              
\usepackage[utf8]{inputenc}                                  
\usepackage{amsfonts}
\usepackage{amsmath} 
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{romannum}
\usepackage{tfrupee}
\providecommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\providecommand{\myvec}[1]{\ensuremath{\begin{bmatrix}#1\end{bmatrix}}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\begin{document}
\section{MATRICES}
\begin{enumerate}
	\item Find the value of $ k $ if $M$ =$ \myvec {1 & 2 \\ 2 & 3 }$  and     $M^2 - kM - I_2 = 0 $
\item Using properties of determinants, prove that:\\

	$ \myvec  {1 + a^2 - b^2 & 2ab & -2b \\ 
 2ab & 1 - a^2 + b^2 & 2a \\
 2b & -2a & 1 - a^2 - b^2}
 = (1 + a^2 + b^2)^3 $
\item  Given two matrices $A$ and $B$:\\
\\
		$A$= \myvec{ 1 & 2 & 3 \\
1 & 4 & 1 \\
		1 & -3 &2}$ and $B$ = \myvec{ 11 & -5 & -14 \\
		-1 & -1 & 2 \\
		-7 & 1 & 6 }$\\

		Find $AB$ and use this result to solve the following system of equations:\\
$x - 2y + 3z = 6,	x + 4y + z = 12,	x - 3y + 2z = 1$
\end{enumerate}
		\section{CIRCLES}
		\begin{enumerate}
			\item Find the equation of an ellipse whose latus rectum is $8$ and eccentricity is $\frac {1}{3}$
			\item Find the equation of the hyperbola whose foci are$(0, \pm \sqrt{10})$ and passing through the point $(2, 3)$.
			\item Show that the rectangle of maximum perimeter which can be inscribed in a circle of radius $10 cm$ is a square of side $10\sqrt{2} cm$.
			\item Find the smaller area enclosed by the circle $x^2 + y^2$ and the line $x + y = 2$.
		\end{enumerate}
		\section{TRIGONOMETRY}
		\title{Questions}
		\begin{enumerate}
			\item Solve: $\cos^{-1}(\sin\cos^{-1} x)$ = $\frac{\pi}{6} $
		\end{enumerate}
		\section{INTEGRATION AND DIFFERENTIATION}
		\begin{enumerate}
\item Evaluate:\\

$ \int \frac{2y^2}{y^2 + 4} dy $ 
\item Evaluate:
	$\int_0^3 f(x) , dx,$ where $\quad  f(x) =\begin{cases}
		\cos2x & 0 \leq x \leq \frac{\pi}{2}, \\3, &  \frac{\pi}{2} \leq x \leq 3.
	\end{cases}$
\item If $y = e^{m \cos^{-1} x}$, prove that:\\
	$ (1 - x^2) \frac{d^2 y}{dx^2} - x \frac{dy}{dx} = m^2 y $
\item Evaluate:\\
	$ \int \frac{\sec x}{1 + \csc x} dx $
\item Solve the differential equation:\\

	$\frac{x}{e^y}\left(1 - \frac{x}{y}\right) + \left(1 + \frac{x}{e^y}\right) \frac{dx}{dy} = 0$ when $x = 0$, $y = 1$.
				
				\item Solve the differential equation:\\
					$\sin^{-1} \left( \frac{dy}{dx} \right) = x + y$
		\end{enumerate}
\section{VECTOR GRAPHS}
\begin{enumerate}
	    \item Using vectors, prove that angle in a semicircle is a right angle.
	    \item Find the volume of a parallelepiped whose edges are represented by the vectors:
		    $\vec{a} = 2\hat{i} - 3\hat{j} - 4\hat{k}$, $\vec{b} = \hat{i} +2\hat{j} - \hat{k}$, $\vec{c} = 3\hat{i} + \hat{j} + 2\hat{k}.$
	    \item Find the equation of the plane passing through the intersection of the planes:
 $  x + y + z + 1 = 0 $  and $ 2x - 3y + 5z - 2 = 0 $ and the point $( -1, 2, 1).$
 \item Find the shortest distance between the line:
	 $ \vec{r} = \hat{i} + 2t\hat{j} + 3t\hat{k} + \lambda(2\hat{i} + 3\hat{j} + 4\hat{k}) $ and $\vec{r} = 2\hat{i} + 4t\hat{j}+ 5t\hat{k} + \mu(4\hat{i} + 6\hat{j} + 8\hat{k}) $
\end{enumerate}
		\section{PROBABILITY}
		\begin{enumerate}
			\item A card is drawn from a well shuffled pack of playing cards.What is the probability that it is either a spade or an ace or both?

			\item An urn contains $2$ white and $2$ black balls. A ball is drawn at random. If it is white, it is not replaced into the urn.Otherwise, it is replaced with another ball of the same colour. The process is repeated. Find the probability that the third ball drawn is black.
			
			\item Three persons $A$, $B$ and $C$ shoot to hit a target. If $A$ hits the target four times in five trials, $B$ hits it three times in four trials, and $C$ hits it two times in three trials, find the probability that:\\ \begin{enumerate}	[label=\roman*)] \item Exactly two persons hit the target.
					\item  At least two persons hit the target.
			\item  None hit the target.
			\end{enumerate}
		\item $Box I$ contains two white and three black balls. $Box II$ contains four white and one black balls, and $Box III$contains three white and four black balls. A dice having three red, two yellow and one green face, is thrown to select the box. If red face turns up,we pick up $Box I,$ if a yellow face turns up we pick $Box II,$ oth    erwise we pick up $Box III.$ Then, we draw a ball from the selected box. If the ball drawn is white, what is the probability that the dice had turned up with a red face?

		\item Six dice are thrown simultaneously. If the occurrence of an odd number on a single dice is considered a success, find the probability of maximum three successes.
		\end{enumerate}
			\section{CORRELATION}
				\begin{enumerate}
			\item  In a contest the competitors are awarded marks out of $20$ by two judges. The scores of the $10$ competitors are given below. Calculate Spearman’s rank correlation.
				\begin{center}
					\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
					\hline
					Competitors & A & B & C & D & E & F & G & H & I & J \\                         
						\hline
					Judge A & 2 & 11 & 11 & 18 & 6 & 5 & 8 & 16 & 13 & 15 \\                        \hline
					Judge B & 6 & 11 & 11 & 9 & 14 & 20 & 4 & 3 & 13 & 17 \\                        \hline
					 \end{tabular}
				\end{center}
			 
			\item The two lines of regressions are $ 4x + 2y - 3 = 0$ and $3x + 6y + 5     = 0 $. Find the correlation co-efficient between $ x $ and $y .$
				\end{enumerate}
				\section{LINEAR EQUATIONS}
						\begin{enumerate}
							
							\item If $ 1,\omega \quad {and} \omega^2 $ are the cube roots of unity, prove that :
								$\frac{a + b\omega + c\omega^2}{c + a\omega + b\omega^2} = \omega^2 $ 
							\item Solve the equation for $x$:
								$ \sin^{-1} \frac{5}{x} + \sin^{-1} \frac{12}{x} = \frac{\pi}{2}, \quad x \neq 0 $
						\end{enumerate}
						\section{ALGEBRA}
						\begin{enumerate}
							\item $A$, $B$, and $C$ represent switches in ‘on’ position and $A'$, $B'$, and $C'$ represent them in ‘off’ position. Construct a switching circuit representing the polynomial $ABC + AB'C' + A'B'C$. Using Boolean Algebra, prove that the given polynomial can be simplified to $C(A + B')$. Construct an equivalent switching circuit.

							\item If $z = x + iy$,$w = \frac{2 - iz}{2z - i}$, and $|\omega| = 1$, find the locus of $z$ and illustrate it in the Argand Plane. 
						\end{enumerate}
						\section{FUNCTIONS}
						\begin{enumerate}
							\item  Verify Lagrange's Mean Value Theorem for the following function:\\
								$f(x) = 2\sin x + \sin 2x \quad \text{on} \quad [0, \pi]$
				\end{enumerate}
				\section{REGRESSION}
				\begin{enumerate}
					\item Given that the observations are:
						\\                                $(9, -4), (10, -3), (11, -1), (12, 0), (13, 1), (14, 3), (15, 5), (16, 8)$. \\ 
						Find the two lines of regression and estimate the value of $y$ when $x = 13.5$.
				\end{enumerate}
				\section{COST AND INTEREST}
				\begin{enumerate}
					\item Mr. Nirav borrowed \rupee $50,000$ from the bank for $5$ years. The rate of interest is $9\%$ per annum compounded monthly. Find the payment he makes monthly if he pays back at the beginning of each month.

					\item A bill for \rupee $7,650$ was drawn on $8\textsuperscript{th} March, 2013, at 7 months$. It was discounted on $18\textsuperscript{th} May, 2013$ and the holder of the bill received \rupee $7,497$. What is the rate of interest charged by the bank?
					
					\item The average cost function, $AC$ for a commodity is given by $AC = x + 5 + \frac{36}{x}$ in terms of output $x$. Find: \begin{enumerate}
							[label=\roman*] 
						\item The total cost, $C$ and marginal cost, $MC$ as a function of $x$. 
						\item The outputs for which $AC$ increases. 
				\end{enumerate}
				\end{enumerate}
						\section{MIXTURES}
						\begin{enumerate}
							\item A dietician wishes to mix two kinds of food $X $and $Y$ in such away that the mixture contains at least $10 units$ of vitamin $A$, $12 units$ of vitamin $B$ and $8 units$ of vitamin $C$. The vitamin contents of one kg of food is given below: 
								\begin{center}
								         \begin{tabular}{|c|c|c|c|} 
	         \hline
	        Food & Vitamin A & Vitamin B & Vitamin C \\ 
							         \hline
									 X & 1 unit & 2 units & 3 units \\
									 \hline
									 
									 Y & 2 units & 2 units & 1 unit \\ 
									
									 \hline
									 
									 \end{tabular}
									 
\end{center} 
						\end{enumerate}
						\section{PROFIT AND LOSS}
						\begin{enumerate}
							\item Calculate the index number for the year $2014,$ with $2010$ as the base year by the weighted aggregate method from the following data:\\
								\begin{center}
								 
$									\begin{tabular}{|c|c|c|c|}
										 \hline
										  Commodity & Price in $2010 (\rupee)$ & Price in $2014 (\rupee)$ & Weight \\
										   \hline
										    A & 2 & 4 & 8 \\
										     \hline 
										      B & 5 & 6 & 10 \\
										      \hline
										       C & 4 & 5 & 14 \\
										 \hline
										  D & 2 & 2 & 19 \\
										   \hline
\end{tabular}$ 
										     \end{center}
							     \item The quarterly profits of a small scale industry (in thousands of rupees) are as follows:
										         \begin{center}  
			$ \begin{tabular}{|c|c|c|c|c|}  
													              \hline
													              Year & Quarter $1$ & Quarter $2$ & Quarter $3$ & Quarter $4$ \\
													             \hline
													              2012 & 39 & 47 & 20 & 56 \\
													                 \hline
													              2013 & 68 & 59 & 66 & 72 \\  
													                  \hline
													             2014 & 88 & 60 & 60 & 67 \\
													              \hline
						\end{tabular}$
											      \end{center}

									Calculate four quarterly moving averages. Display these and the original figures graphically on the same graph sheet.

						\end{enumerate}
						\section{LIMITS}
						\begin{enumerate}
					\item Using L'Hospital's rule, evaluate: 
							$\lim_{x \to 0} \frac{x - \sin x}{x^2 \sin x}$
\end{enumerate}				

				\end{document}
